### 2016-12-19 doc/paper/paper.tex
minor changes

\[
\mathcal{F}(n) = ...
\]

@@

@@

>>>>

\[
\mathcal{F}(n) = 
\]

\[
\mathcal{F}^*(n) = \mathcal{F}(n) + \lambda * \mathcal{F}(n_e)
\]

@@

For the purpose of validation we selected two classes of programs. The first class only includes JS programs composed of the primitive types. The programs in the second class additionally accept arguments of the DOM type. We collected those program from several researches in the field of web application analysis, and JS in particular. Moreover, we introduced few other subjects found in open source such as \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}}.

@@

\subsection{Limitations}
\label{sub.sec.eval.limit}

Our framework imposes certain constraints on the structure of JS programs:
\begin{itemize}
\item no inter-procedural function calls
\item no recursion  
\end{itemize}
